Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-10-11 Multilevel Missing Data/Multilevel-Missing-Data.tex

\begin{itemize}
\item
  Waarom zijn standaard (ad hoc) methoden niet geschikt?
\item
  Wat is heterogeniteit? (i.e.~variability binnen studies
  vs.~variability tussen studies). Random effects voor intercept term,
  predictor effects, en/of variance residual error
\item
  JOMO aanpak (misschien buiten beschouwing laten?)
\item
  MICE aanpak: one-stage imputation versus two-stage imputation methods
\item
  Imputatie van studie-level versus patient-level covariates
\item
  Omgaan met MNAR
\end{itemize}

>>>>

\begin{itemize}
\item
  Why are standard (ad hoc) methods not well suited?
\item
  What is heterogeniety? (i.e.~variability within studies
  vs.~variability between studies). Random effects for intercept term,
  predictor effects, and/or variance residual error
\item
  Systematic vs sporadic missingness
\item
  MICE approach: one-stage imputation versus two-stage imputation
  methods
\item
  Imputation of study level versus patient-level covariates
\item
  Handling MNAR
\item
  Case study: metamisc::impact()
\end{itemize}

\hypertarget{think-about-adding}{%
\section{Think about adding}\label{think-about-adding}}

\begin{itemize}
\tightlist
\item
  JOMO in mice
\end{itemize}
